Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-21 paper/v2/paper-edited.tex
more edits
another minor change

\begin{algorithm}[t!]
\caption{Inferring regret-free preferences}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
  \If {$loc(N_1) \neq loc(N_2)$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \If {$n_1 \nleq_{rank} n_2$}
      \Return false
    \EndIf
    \For {$n_2'$ in adj($G$, $n_2$)}
      \If {\big($\exists n_1' \in \textup{adj}(G,n_1), n_1' \approx n_2'$\big) \textbf{or} \\
            \hspace{5.2em} 
            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1'$\big)}
        \If {$(x,y)$ not marked}
          \State {mark $(x,y)$ as seen}
          \State $q.Enqueue(x,y)$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile
  \Return true
  \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

To avoid this situation, the compiler checks that, any time we have two shadows $N_1$ and $N_2$ for some topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (that is, $N_1 <_{lp} N_2$). The idea is that any time $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway.
%
For example, $(D,2,2)$ appears ``above'' $(D,-,2)$, so we require that $(D,2,2) <_{lp} (D,-,2)$. In this case, the compiler determines that this is safe according to Algorithm~\ref{alg:failures}, so router $D$ can simply prefer advertisements from $Y$ and $X$ over advertisements from $C$.

>>>>

\begin{algorithm}[t!]
\caption{Inferring regret-free preferences}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
  \If {$N_1 \not\approx N_2$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \If {$n_1 \nleq_{rank} n_2$}
      \Return false
    \EndIf
    \For {$n_2'$ in adj($G$, $n_2$)}
      \If {\big($\exists n_1' \in \textup{adj}(G,n_1), n_1' \approx n_2'$\big) \textbf{or} \\
            \hspace{5.2em} 
            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1$\big)}
        \If {$(x,y)$ not marked}
          \State {mark $(x,y)$ as seen}
          \State $q.Enqueue(x,y)$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile
  \Return true
  \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

To avoid this situation, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (i.e., $N_1 <_{lp} N_2$). The idea is that any time shadow $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway and will only be better off.
%
For example, $(D,2,2)$ appears ``above'' $(D,-,2)$, so we require that $(D,2,2) <_{lp} (D,-,2)$. In this case, the compiler determines that this is safe according to Algorithm~\ref{alg:failures}, so router $D$ can simply prefer advertisements from $Y$ and $X$ over advertisements from $C$.
